### 2019-09-11 scache/tii/tex/optimization.tex
Revision for re-submit.

\section{Shuffle Optimization}
\label{opt}
This section presents the detailed methodologies to achieve the three design goals. 
The out-of-framework shuffle data management is used to decouple shuffle from execution and provide a cross-framework optimization. 
Two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) and a co-scheduler is used to achieve shuffle data pre-fetching without launching tasks.

@@

\subsection{Decouple Shuffle from Execution}
To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
To prevent the release of a slot being blocked by shuffle write,  
SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
% After the memory copy, the slot will be released immediately.

From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
With the precondition of shuffle data pre-fetching, 
the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.

\subsection{Pre-scheduling with Application Context}
The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
% Once the tasks are scheduled, the slots will be occupied to launch them. 
And the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling.

\subsubsection{Problem of Random Mapping}\label{randomassign}
The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
We use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% The average shuffle read time is $3.2\%$ of total reduce completion time.
We remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
The performance of random mapping drops as the round number grows. 
% Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

\begin{figure}
	% \centering
	% \begin{subfigure}[b]{0.31\linewidth}
	% 	\includegraphics[width=\linewidth]{fig/hash_pre}
	% 	\caption{Linear Regression Prediction of Hash Partitioner\newline}
	% 	\label{fig:hash_pre}
	% \end{subfigure}
	\begin{subfigure}[b]{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
		% \vspace{1em}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	% \vspace{-1em}
\end{figure}

@@

{\color{black}

@@

the shuffle data size can be predicted accurately by a liner regression model based on the observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}.

@@

However, the linear regression model can fail in some uncertainties introduced by sophisticated frameworks like Spark. 
For instance, the customized partitioner may result in large inconsistency between observed map output blocks distribution and the final reduce input distribution. 
We present a particular example with 20 tasks respectively in Figure \ref{fig:range_pre_sample}. 
The data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew. 

@@

% That is, for one reduce task, almost all of the input data are produced by a particular map task (e.g., the observed map tasks only produce data for reduce task 0-5 in Figure \ref{fig:range_pre_sample}).
% The data locality skew results in a missing of other reduce tasks' data in the observed map outputs.

To handle this corner case, we introduce another methodology, named \textit{weighted reservoir sampling}, as a substitution of linear regression. 
Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data. 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
The $inputSize_j$ is the input size of $j$th map task. 
Note that sampling does not consume the input data of map tasks. 
Figure \ref{fig:prediction_relative_error} proves that the sampling prediction can provide much more accurate result than the linear regression. 
% The $BlockSize_{ji}$ can be calculated by:
% \begin{equation}
% \label{equationsample}
% \begin{aligned}
% 	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
% 	sample_i &= \text{number of samples for $reduce_i$}
% \end{aligned}
% \end{equation}
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
% On the other hand, the result of linear regression comes out with a large relative error. 
% Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
% {\color{black}

@@

% During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
% \begin{equation}
% \label{equationprob}
% \begin{aligned}
% 	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
%     m &= \text{number of map tasks}
% \end{aligned}
% \end{equation}
% This parameter is used to achieve a better data locality while performing shuffle pre-scheduling. 
}

\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
% But ignoring the data locality can introduce extra network transfer. 
% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
{\color{black}
To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}). For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum. 
}
Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.

@@

% It means the $SWAP\_TASKS$ can help revise the scheduling to match the previous mapping as much as possible while maintaining the good load balance.

% As for the input of $SCHEDULE$ function in Algorithm \ref{hminheap}, $m$ is the partition number of input data; $h$ is the array of nodes ID in cluster; $p\_reduces$ is the predicted reduce matrix. Each row in $p\_reduces$ contains $rid$ as reduce partition ID; $size$ as predicted size of this partition; $prob$ as the maximum composition portion of reduce data; $host\_id$ as the node ID that produces the maximum portion of reduce data, and $assigned\_id$ as the node ID assigned by Algorithm \ref{hminheap}. As for $M$, it is consists $host\_id$, an array of $reduce$ scheduled on this node and the $size$ of them.

>>>>

\section{Shuffle Optimization}
\label{opt}
This section presents the detailed methodologies to achieve shuffle optimization. 
{\color{blue}
Firstly, we discuss the reason causes shuffle overhead in the DAG frameworks.
In the following subsection, we propose a shuffle data management system to decouple shuffle from execution. 
And we propose the pre-scheduling and pre-fetching to hide shuffle overhead into multi-round map tasks.
Furthermore, two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) are used to improve the accuracy of prediction in the pre-scheduling.
}

% The out-of-framework shuffle data management is used to decouple shuffle from execution and provide a cross-framework optimization. 
% Two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}) and a co-scheduler is used to achieve shuffle data pre-fetching without launching tasks.

@@

\begin{figure}
	% \centering
	% \begin{subfigure}[b]{0.31\linewidth}
	% 	\includegraphics[width=\linewidth]{fig/hash_pre}
	% 	\caption{Linear Regression Prediction of Hash Partitioner\newline}
	% 	\label{fig:hash_pre}
	% \end{subfigure}
	\begin{subfigure}[b]{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
		% \vspace{1em}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	% \vspace{-1em}
\end{figure}

{\color{blue}
\subsection{Observations}\label{observation}
% DAG - shuffle - couple \& dependency - overhead in job - formula - how to optimize? - decouple \& pre-fetch - memory

In distributed computing, we use shuffle to do all-to-all data transfer among the nodes.
For a clear illustration, we divide a computing job into three phases: map, shuffle, and reduce phase.
In most of the DAG frameworks, including Spark, Hadoop MapReduce, and Tez, shuffle phase is couple with reduce phase which means that shuffle data transfer and reduce computing start simultaneously.
On the reduce side, the shuffle data transfer introduces an explicit overhead during shuffle read.
Because the reduce computing depends on the shuffle results, the waiting for the shuffle data causes the overhead.
Furthermore, because all reduce tasks start shuffle read simultaneously, the synchronized shuffle read causes a burst of network traffic and further enlarge the overhead.

% To better illustrate the shuffle optimization, we use this formula to represent the job completion time: \(T_{Job}=T_{Map}+T_{Reduce}+T_{overhead}\). \(T_{Map}\) represents the completion time of map phase and \(T_{Reduce}\) represents the reduce phase time without being affected by the coupled shuffle phase. 
% We use \(T_{overhead}\) to represent the above-mentioned overhead caused by shuffle.
% In the following subsections, we introduce how we decouple the shuffle and use pre-fetching and memory cache to mitigate the overhead.
To mitigate the shuffle overhead, we propose an optimization that starts shuffle read ahead of reduce phase to overlap the shuffle data transfer in multi-round map tasks, and uses memory to cache the shuffle data. To achieve this optimization:
\begin{itemize}
	\item Shuffle phase should be decoupled from reduce phase to achieve a better scheduling scheme.
	\item Reduce tasks should be pre-scheduled in map phase to achieve shuffle data pre-fetching.
\end{itemize}
% In Section \ref{model}, we also propose a performance model called the FRQ to model the optimization.
}

\subsection{Decouple Shuffle from Execution}
{\color{blue}
To decouple the shuffle from reduce tasks, we propose a shuffle data management system called SCache to take over all shuffle data from the DAG frameworks.
SCache provides two APIs named $putBlock$ and $putBlock$ to manage the shuffle data.
On the map side, after shuffle data blocks are produced, the map task uses $putBlock$ to transfer the data blocks to SCache instead of keeping them on local storage.
Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
SCache gets the shuffle data as soon as the end of a map task's execution and starts to shuffling data immediately.
% SCache leverages the property of multi-round tasks to 
On the reduce side, due to the shuffle data pre-fetching of SCache, the reduce task use $getBlock$ to get the shuffle data from the local memory of SCache.

SCache takes over all shuffle data and keep them on the memory instead of storing on disk liked the DAG frameworks.
In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
}
% To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% To prevent the release of a slot being blocked by shuffle write,  
% SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
% After the memory copy, the slot will be released immediately.

% From the perspective of reduce task, SCache provides an API named $getBlock$ to replace the original implementation of shuffle read. 
% With the precondition of shuffle data pre-fetching, 
% the $getBlock$ leverages the memory copy to fetch the shuffle data from the local memory of SCache.

% \subsection{Pre-scheduling with Application Context}
{\color{blue}
\subsection{Pre-scheduling and Pre-fetching Shuffle Data}
% multi-round -> how to optimize? -> pre-schedule -> pre-fetch -> formula
The pre-scheduling and pre-fetching are the most critical aspects of the optimization.
Multi-round tasks execution is used to gain better parallelism in most of DAG frameworks. For example, Spark recommends 2-3 tasks per CPU core in tasks configuration.
Since shuffle data is available as soon as the map task finished, and the network is idle in map phases, 
SCache starts pre-fetching and hides shuffle overhead into multi-round map tasks.
However, the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
To pre-scheduling the mapping, we propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
The DAG frameworks follow the co-scheduler to starts reduce tasks.
}
% The pre-scheduling and pre-fetching are the most critical aspects of the optimization. 
% The task-node mapping is not determined until tasks are scheduled by the scheduler of DAG framework. 
% Once the tasks are scheduled, the slots will be occupied to launch them. 
% And the shuffle data cannot be pre-fetched without the awareness of task-node mapping.
% We propose a co-scheduling scheme with two heuristic algorithms (Algorithm \ref{hminheap}, \ref{mhminheap}). 
% That is, the task-node mapping is established a priori, and then it is enforced by the co-scheduler when the DAG framework starts task scheduling.

\subsubsection{Problem of Random Mapping}\label{randomassign}
{\color{blue}
% Mapping tasks to nodes randomly and evenly is the simplest pre-scheduling way.
To evaluate the performance of scheduling strategies, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
The performance of random mapping drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly mapping also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.
}
% The simplest way of pre-scheduling is mapping tasks to nodes randomly and evenly. 
% We use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% In order to evaluate the effectiveness of random mapping, we use traces from OpenCloud\footnote{\label{fn:trace}http://ftp.pdl.cmu.edu/pub/datasets/hla/dataset.html} for the simulation.
% The average shuffle read time is $3.2\%$ of total reduce completion time.
% We remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
% As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
% The performance of random mapping drops as the round number grows. 
% Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
% This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
% Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
% In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

{\color{blue}

@@

the shuffle output can be predicted accurately by a linear regression model based on the observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}.

@@

However, the linear regression model can fail in some scenarios. 
For example, some customized partitions may cause large inconsistency between observed map output distribution and the final reduce input distribution. 
To illustrate the case, we present a particular spark job which using the Spark RangePartitioner in Figure \ref{fig:range_pre_sample}. 
The observed map outputs are picked randomly. 
The job uses the Spark RangePartitioner and introduce an extreme high data skew.
Due to the extreme high data skew introducing by the partition, linear regression model cannot fit the result well.
% The data partitioned by Spark RangePartitioner in Figure \ref{fig:range_pre_sample} results in a deviation from the linear regression model, because the RangePartitioner might introduce an extreme high data locality skew. 

@@

That is, for one reduce task, almost all of the input data are produced by a particular map task (e.g., the observed map tasks only produce data for reduce task 0-5 in Figure \ref{fig:range_pre_sample}).
The data locality skew results in a missing of other reduce tasks' data in the observed map outputs.

To solve this problem, we propose a new methodology named \textit{weighted reservoir sampling}.
SCache uses this method instead of the linear regression to predict output when using a RangePartitioner or a customized non-hash partitioner.
% we introduce another methodology, named \textit{weighted reservoir sampling}, as a substitution of linear regression. 
% Note that linear regression will be replaced only when a RangePartitioner or a customized non-hash partitioner occurs. 
For each map task, we use classic reservoir sampling to randomly pick $s \times p$ of samples, where $p$ is the number of reduce tasks and $s$ is a tunable number. 
After that, the map function is called locally to process the sampled data. 
Finally, the partitioned outputs are collected with the $InputSize_j$ as the weight of the samples.
The $inputSize_j$ is the input size of $j$th map task. 
% Note that sampling does not consume the input data of map tasks. 
The $BlockSize_{ji}$ can be calculated by:
\begin{equation}
\label{equationsample}
\begin{aligned}
	BlockSize_{ji} &= {{InputSize_j \times \frac{sample_i}{s \times p}}} \\
	sample_i &= \text{number of samples for $reduce_i$}
\end{aligned}
\end{equation}
In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide a much more accurate result than the linear regression. 
% The classic reservoir sampling is designed for randomly choosing \textit{k} samples from \textit{n} items, where \textit{n} is either a very large or an unknown number \cite{reservoir}. 
% In Figure \ref{fig:range_pre_sample}, when $s$ is set to $3$, the result of sampling prediction is much better than linear regression. 
% The variance of the normalization between sampling prediction and reduce distribution is because the standard deviation of the prediction results is relatively small compared to the average prediction size, which is $0.0015$ in this example. 
% Figure \ref{fig:prediction_relative_error} further proves that the sampling prediction can provide precise result even in the dimension of absolute input size of reduce task. 
% On the other hand, the result of linear regression comes out with a large relative error. 
% Though the weighted reservoir sampling is precise, it also introduces extra overhead. 
% We will show the overhead evaluation of sampling in Section \ref{evaluation}.
% {\color{black}

@@

}
During both of the predictions, the composition of each reduce partition is calculated as well. We define $prob_i$ as
\begin{equation}
\label{equationprob}
\begin{aligned}
	prob_i &= \max_{0 \leq j \leq m} \frac{BlockSize_{kji}}{reduceSize_i} \\
    m &= \text{number of map tasks}
\end{aligned}
\end{equation}
This parameter is used to achieve a better data locality while performing shuffle pre-scheduling.

\subsubsection{Heuristic MinHeap Scheduling}\label{h-minheap}
% As long as the input sizes of reduce tasks are available, the pre-scheduling is a classic scheduling problem without considering the data locality. 
% But ignoring the data locality can introduce extra network transfer. 
% In order to balance load while minimizing the network traffic, we present the Heuristic MinHeap Scheduling algorithm (Algorithm \ref{hminheap}).
To balance load while minimizing the network traffic, we present the \textit{Heuristic MinHeap Scheduling} algorithm (Algorithm \ref{hminheap}).
{\color{blue}
% For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum. 
To keep the pre-scheduling load balance, we maintain a min-heap in the first $while$ loop (i.2., line $6-11$).
We use the min-heap to simulate the load of each node and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum.
Spark FIFO only can achieve $2\text{-}approximation$ optimum.
}
% Since the sizes of tasks are considered while scheduling, \textit{Heuristic MinHeap Scheduling} can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
% Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.

{\color{blue}
As shown in Figure \ref{fig:sim}, \textit{Heuristic MinHeap Scheduling} has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
Since the algorithm only maintains a min-heap and traverses $reduce$ for swapping, the algorithm needs $O(n)$ operations.
}

To traverse $reduce$ for accumulating previous $shuffle$ and re-shuffling data, the algorithm needs $O(n)$ operations.

@@
